---
title: "My elaborated analysis"
author: "Martin Hinz"
date: '`r format(Sys.Date())`'
output: bookdown::pdf_document2
lot: yes
lof: yes
bibliography: bib.bib
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Analyses

## First function

For doubling the number, you might use the function 'double_me'.

```{r}
library(coursepackageberlin)
a <- 2
double_me(a)

```

See this visual (\@ref(fig:chunk-label)):


```{r chunk-label, echo = FALSE, fig.cap = 'A figure caption.'}
test <- data.frame(x=1:100)
test$y <- double_me(test$x)
plot(test, type="l")

```

# Challenge

1. simple table and plot
2. add captions and crossref to those
3. add bib file and cite
4. Add second simple function to R/
5. + test
6. pass tests


# Solution

We simulate a number of characters:

```{r }
my_letters <- sample(letters, size = 500, replace = T)
```

now we table that

```{r }
table(my_letters)
```

and in more beautiful

```{r letter-table}
knitr::kable(as.data.frame(table(my_letters)), caption = "Letter frequency table")
```
and plot frequency

```{r letter-plot, fig.cap = 'Letter frequency'}
my_plot_letters <- table(my_letters)
barplot(my_plot_letters)
```

see solution table (\@ref(tab:letter-table)) and figure (\@ref(fig:letter-plot)). for more information consult [@R-base].

Sampling letters can also be archieved by a function:


```{r}
my_new_letters <- sample_letters(50)
```

We can use that to make a lorem ipsum

```{r lorem_ipsum, cache=T}
x <- make_lorem_ipsum(100)
x
```

and reuse it
```{r lorem_ipsum_2, dependson="lorem_ipsum"}
cat(paste(rep(x,10), collapse = "\n"))
```


use binford
```{r binford, dependson="lorem_ipsum"}
library(binford)
```


# Point Pattern
Load data

```{r}
harran <- read.csv("Sites_HarranPlain.txt")
```

Create point pattern from date, first transform from WGS Lat/Lng to something useful

```{r}
library(spatstat)
library(sp)

coordinates(harran) <- ~X+Y

proj4string(harran) <- CRS("+init=epsg:4326")

harran <- spTransform(harran, CRSobj = CRS("+init=epsg:32637"))

harran_ppp <- ppp(x = coordinates(harran)[,1],
                  y = coordinates(harran)[,2],
                  window = owin(xrange = bbox(harran)[1,],
                  yrange = c(min(harran@coords[,2]),min(harran@coords[,2]+60000))))
str(harran_ppp)
```


Plot the resulting point pattern

```{r}
plot(harran_ppp)
```

## challenge: delete dublicated points
```{r}

harran_ppp_cleaned <- harran_ppp[!duplicated.ppp(harran_ppp)]
plot(harran_ppp_cleaned)
```
## nearest neighbour

```{r}
harran_ppp_nn <- nndist(harran_ppp_cleaned)
hist(harran_ppp_nn)
```

## next challenge: kde

```{r}
harran_kde <- density.ppp(harran_ppp_cleaned, sigma = mean(harran_ppp_nn))
plot(harran_kde)
```

## dem 

```{r}

library(raster)
dem <- raster("dem.tif")
image(dem)

im_dem <- as.im(as.image.SpatialGridDataFrame(as(dem, "SpatialGridDataFrame")))
```
## rhohat

```{r}
harran_rhohat <- rhohat(object = harran_ppp_cleaned, covariate = im_dem)
plot(harran_rhohat)
```

## predicition
```{r}
diffrho

plot(predict(harran_rhohat))

diff_rho <- harran_kde - predict(harran_rhohat)


```

## compare to poisson

```{r}
density_orig <- harran_ppp_cleaned$n/area.owin(harran_ppp_cleaned$window)
pois_ppp <- rpoispp(density_orig, win = harran_ppp_cleaned$window)

plot(pois_ppp)
```

