---
title: "My elaborated analysis"
author: "Martin Hinz"
date: '`r format(Sys.Date())`'
output: bookdown::pdf_document2
lot: yes
lof: yes
bibliography: bib.bib
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Analyses

## First function

For doubling the number, you might use the function 'double_me'.

```{r}
library(coursepackageberlin)
a <- 2
double_me(a)

```

See this visual (\@ref(fig:chunk-label)):


```{r chunk-label, echo = FALSE, fig.cap = 'A figure caption.'}
test <- data.frame(x=1:100)
test$y <- double_me(test$x)
plot(test, type="l")

```

# Challenge

1. simple table and plot
2. add captions and crossref to those
3. add bib file and cite
4. Add second simple function to R/
5. + test
6. pass tests


# Solution

We simulate a number of characters:

```{r }
my_letters <- sample(letters, size = 500, replace = T)
```

now we table that

```{r }
table(my_letters)
```

and in more beautiful

```{r letter-table}
knitr::kable(as.data.frame(table(my_letters)), caption = "Letter frequency table")
```
and plot frequency

```{r letter-plot, fig.cap = 'Letter frequency'}
my_plot_letters <- table(my_letters)
barplot(my_plot_letters)
```

see solution table (\@ref(tab:letter-table)) and figure (\@ref(fig:letter-plot)). for more information consult [@R-base].

Sampling letters can also be archieved by a function:


```{r}
my_new_letters <- sample_letters(50)
```

We can use that to make a lorem ipsum

```{r lorem_ipsum, cache=T}
x <- make_lorem_ipsum(100)
x
```

and reuse it
```{r lorem_ipsum_2, dependson="lorem_ipsum"}
cat(paste(rep(x,10), collapse = "\n"))
```


use binford
